---
title: "In-Class Work"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')

dat = ggplot2::diamonds
```


Display first 10 rows of `dat` dataset
```{r}
  head(dat, 10)
```


Create a chart to look at the distribution of `price`
```{r}
  ggplot(data = dat, mapping=aes(x = price)) +
    geom_histogram(bins = 15)
  
```

Create a chart to look at the distribution of `price` broken down by `clarity`
```{r}
ggplot(data = dat, mapping=aes(x = price)) +
    geom_histogram(bins = 10)+
    facet_wrap(~clarity, scales = 'free_y')
```

Create a different chart to illustrate the same thing as above
```{r}
ggplot(data = dat, mapping=aes(x = price)) +
    geom_density() +
    facet_wrap(~clarity, scales = 'free_y')
```

Examine variables: `x`, `y`, and `z` -- what do you notice?
```{r}
ggplot(dat, aes(x = z, y = y)) +
  geom_point()
```


Show the relationship between `carat` and `price`  --  fit a curve to it
```{r}
ggplot(dat, aes(x = carat, y = price)) +
  geom_point() +
  geom_smooth()
```

How does your curve look? Could you change the function it uses to use a linear model?
```{r}
ggplot(dat, aes(x = carat, y = price)) +
  geom_point() +
  geom_smooth(method = 'lm')
```



Create 3 more plots that you think are interesting.
Add a title, subtitle, labels, and a caption where they make sense
```{r}
ggplot(dat, aes(x = carat, y = price)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  labs(title = 'diamonds')
```

```{r}
ggplot(dat, aes(x = carat, y = price)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  labs(title = 'diamonds')
```

```{r}
ggplot(dat, aes(x = carat, y = price)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  labs(title = 'diamonds', subtitle = 'your best friend', caption = 'the right-hand corner') +
  xlab('x-label override') + 
  ylab('y-label override')
  
```
```{r}

```


